Verifying Demonstrations

### 2019-05-28 paper/DB-anon-cred.tex
Edits intro to DB-anon-cred

\section{Distance-bounding anonymous credentials}%
\label{DB-anon-cred}

One protocol exists in the literature that provides \acp{PPK} with most of the desired properties described previously, ProProx~\cite{ProProx}\footnote{Note that~\cite{ProProx} uses the abbreviation PoPoK, we prefer \acs{PPK} for shorter notation.}.
ProProx is secure against a malicious verifier, but it provides \iac{PPK} protocol for quadratic residues (\ie protocols of the form \(\PPK[\alpha][a = 
  \alpha^2]\)), while in our context, we need \iac{PPK} protocol for discrete logarithms (\ie \(\PPK[\alpha][a = g^\alpha]\)) due to our choice of anonymous credentials whose desirable properties we list in \cref{ZK-anon-cred}.%, which in turn is due to their \ac{PRF} for deriving identifiers from a long-term ID with unlinkability to the original ID but with proof of validity of this derivation. 
To realize this, we will now introduce such a protocol to enable us to have \ac{DB} anonymous credentials.

@@

In the original \ac{DB} paper by \citet{DistanceBounding}, one of the distance-bounding protocols is based on the Schnorr identification scheme~\cite{Schnorr}.
However, this \ac{DB} Schnorr protocol was shown to be prone to distance hijacking~\cite{DistanceHijacking, TamarinDB}, in addition to not being secure against terrorist fraud.
We now propose another way to turn the Schnorr protocol into a public-key \ac{DB} protocol that is secure against \ac{DBMF}, \ac{DBDF}, \ac{DBDH} and \ac{DBTF}.
It is important in our setting that the protocol is a public-key protocol, both to reach strong privacy properties and also because this property implies protection against an impersonating verifier.

>>>>

\section{Distance-bounding \ac*{ZKPK} for discrete logarithms}%
\label{DB-anon-cred}

We will now introduce \iac{DB} protocol which is a \ac{ZKPK} for discrete 
logarithms.
Our protocol is an adaptation of the Schnorr identification 
scheme~\cite{Schnorr}, albeit different from that of 
\textcite{DistanceBounding} in the original \ac{DB} paper.
(That protocol was shown to be prone to distance 
hijacking~\cite{DistanceHijacking,TamarinDB} and was not secure against 
terrorist fraud.)
We propose another way to turn the Schnorr protocol into a public-key \ac{DB} 
protocol which is \iac{ZKPK} that is secure against \ac{DBMF}, \ac{DBDF}, 
\ac{DBDH} and \ac{DBTF}.
This yields strong privacy properties and protection against a malicious, 
impersonating verifier.

We also deviate from the normal technique of one-bit challenges and responses 
otherwise used in \ac{DB} protocols.
\Textcite{UWBwithPulseReordering} proposed a secure encoding for the physical 
layer which removes the requirement of only using single-bit challenges and 
responses for distance bounding.
However, their protocol only works for relay attacks and cannot handle distance 
fraud.
This is due to a requirement of the protocol that the prover and verifier must 
share a secret, and thus must be mutually trusted.

We will first present our version of the \ac{DB} Schnorr protocol for the 
mutual-trust case, where the prover and verifier have a pre-shared secret.
Then we will adapt it by introducing \iac{AKE}.
The authentication in this \ac{AKE} will leverage that our protocol is \iac{DB} 
\ac{ZKPK} for discrete logarithms.
If the \ac{AKE} is based on discrete logarithms we can prove the distance bound 
while we authenticate the key.
This allows us to embed this protocol into tamper resistant hardware to provide 
security against malicious provers.

@@

### 2019-05-28 paper/related-work.tex
Edits intro to DB-anon-cred

>>>>

\subsection{Distance bounding}

One protocol exists in the literature that provides \acp{PPK} with most of the 
desired properties described previously, ProProx~\cite{ProProx}\footnote{Note 
  that~\cite{ProProx} uses the abbreviation PoPoK, we prefer \acs{PPK} for 
  shorter notation.}.
ProProx is secure against a malicious verifier, but it provides \iac{PPK} protocol for quadratic residues (\ie protocols of the form \(\PPK[\alpha][a = 
  \alpha^2]\)), while in our context, we need \iac{PPK} protocol for discrete 
logarithms (\ie \(\PPK[\alpha][a = g^\alpha]\), see \cref{ZK-anon-cred} for 
details).
To realize this, we will now introduce such a protocol to enable us to have 
\ac{DB} anonymous credentials.
